---
title: "ABX scores"
output:
  html_document:
    df_print: paged
---

```{r, message=FALSE}
library(magrittr)
mngu0_mfcc <- readr::read_csv("abx_scores/mngu0_mfcc_test_abx.csv")
mngu0_art <- readr::read_csv("abx_scores/mngu0_ema_15_test_abx.csv")
mngu0_mlp <- readr::read_csv("abx_scores/mngu0_mlp_mngu15_15_test_abx.csv")
mngu0_rnn <- readr::read_csv("abx_scores/mngu0_rnn_mngu15_15_test_abx.csv")
mocha_mfcc_allspk <- readr::read_csv("abx_scores/mocha_mfcc_test_abx.csv")
mocha_art_allspk <- readr::read_csv("abx_scores/mocha_ema_15_test_abx.csv")
mocha_mfcc_withinspk <- readr::read_csv("abx_scores/mocha_mfcc_test_byspk_abx.csv")
mocha_art_withinspk <- readr::read_csv("abx_scores/mocha_ema_15_test_byspk_abx.csv")

mocha_rnn_multi_allspk <- readr::read_csv("abx_scores/mocha_rnn_multi15_15_test_abx.csv")
mocha_rnn_multi_withinspk <- readr::read_csv("abx_scores/mocha_rnn_multi15_15_test_byspk_abx.csv")
```

Within-corpus, within-speaker (MNGU0: one speaker); added additional dimensions (15: hand-coded voicing; x/y for velum, reconstructed)



Overall mean ABX  for MFCC: `r mean(mngu0_mfcc$score)`

Overall mean ABX  for articulatory: `r mean(mngu0_art$score)`



Overall mean ABX  for MLP: `r mean(mngu0_mlp$score)`

Overall mean ABX  for RNN: `r mean(mngu0_rnn$score)`


Within-corpus, speaker-indifferent (MOCHA: two speakers) (added additional dimensions??)



Overall mean ABX  for MFCC: `r mean(mocha_mfcc_allspk$score)`

Overall mean ABX  for articulatory: `r mean(mocha_art_allspk$score)`


Within-corpus, within-speaker (MOCHA: two speakers) (added additional dimensions??)



Overall mean ABX  for MFCC: `r mean(mocha_mfcc_withinspk$score)`

Overall mean ABX  for articulatory: `r mean(mocha_art_withinspk$score)`


Multi-corpus training (??), predicting MOCHA



Overall mean ABX  for RNN, all speakers: `r mean(mocha_rnn_multi_allspk$score)`

Overall mean ABX  for RNN, within speaker: `r mean(mocha_rnn_multi_withinspk$score)`


```{r}
art_vs_mfcc <- mocha_mfcc_allspk %>% dplyr::rename(mfcc_score=score) %>%
  dplyr::inner_join(mocha_art_allspk) %>%
  dplyr::rename(art_score=score) %>%
  dplyr::mutate(diff=(art_score-mfcc_score)) %>%
  dplyr::group_by(phone_1, phone_2) %>%
  dplyr::summarize(diff=mean(diff), art_score=mean(art_score),
                   mfcc_score=mean(mfcc_score)) %>%
  dplyr::ungroup()

ggplot2::ggplot(dplyr::filter(art_vs_mfcc, diff >= 0.6),
                ggplot2::aes(y=art_score, x=mfcc_score,
                             label=paste(phone_1, phone_2, sep=":"))) +
  ggplot2::geom_text() +
  ggplot2::geom_smooth(method="lm")

ggplot2::ggplot(art_vs_mfcc, ggplot2::aes(x=diff)) +
  ggplot2::geom_histogram()

```